SCM plan for a troubling company

### 2012-01-11 article.tex
Write some moar

One of The Problem Company's problems is that they spend more and more time on resolving merge conflicts.
This could be the problem caused by a wrong branch pattern.

>>>>

As the company hasn̈́'t used any form of SCM-tool previously explicit branching didn't exist.
The copying of code between subgroups working on different modules however created implicit branches whenever two version weren't in sync. This creates an implicit feature branch model with merges at each release and sometimes in between but not very often as those merges are hard to
